Evaluating Cultural Transmission in Bronze Age burial rites of Central, Northern and North-western Europe using radiocarbon data

### 2019-03-17 article/02_Materials_and_Methods.Rmd
added simple sed time series plot without simulation results -- still useful

>>>>

\begin{figure}
\centering
\includegraphics[width=\columnwidth]{../analysis/figures/sed_time_series.jpeg}
\caption{\label{simulation}Development of correlation between cultural and spatial distance. The results for the burial customs data (Table \ref{tab:distanceandcorrelationtable*} AB) are displayed with a solid (\textit{burial type}) and dashed (\textit{burial construction}) line. The horizontal line marks the correlation coefficient of zero, where neither positive nor negative correlation can be assumed.}
\end{figure}
